---
title: "PG4"
author: "-Anagha"
date: "11/6/2020"
output: ioslides_presentation
runtime: shiny
---

## I
- URL: *https://github.com/anaghahebbar/PG4*
Find here all the data that have been use for this presentation and also for the first part of the data Science Project.
---

## mtcars Dataset

### Source
```{r,echo=FALSE}
library(datasets)
head(mtcars, 3)
```


## D-Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

## IGNORE
```{r,echo=FALSE}

library(stringi)
sprintf("%s%s%s", stri_rand_strings(100, 5, '[A-Z]'),
      stri_rand_strings(50, 40, '[0-9]'), stri_rand_strings(50, 100, '[A-Z]'))

```


## Analysis - UI Code
```{r,echo=FALSE}
library(shiny)
library(datasets)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
    
    formulaText <- reactive({
        paste("mpg ~", input$variable)
    })
    
    formulaTextPoint <- reactive({
        paste("mpg ~", "as.integer(", input$variable, ")")
    })
    
    fit <- reactive({
        lm(as.formula(formulaTextPoint()), data=mpgData)
    })
    
    output$caption <- renderText({
        formulaText()
    })
    
    output$mpgBoxPlot <- renderPlot({
        boxplot(as.formula(formulaText()), 
                data = mpgData,
                outline = input$outliers)
    })
    
    output$fit <- renderPrint({
        summary(fit())
    })
    
    output$mpgPlot <- renderPlot({
        with(mpgData, {
            plot(as.formula(formulaTextPoint()))
            abline(fit(), col=2)
        })
    })
    
})

```

## Analysis - Server Code
```{r,echo=FALSE}
library(shiny)

shinyUI(
    navbarPage("Shiny Application",
               tabPanel("Analysis",
                        fluidPage(
                            titlePanel("The relationship between variables and miles per gallon (MPG)"),
                            sidebarLayout(
                                sidebarPanel(
                                    selectInput("variable", "Variable:",
                                                c("Number of cylinders" = "cyl",
                                                  "Displacement (cu.in.)" = "disp",
                                                  "Gross horsepower" = "hp",
                                                  "Rear axle ratio" = "drat",
                                                  "Weight (lb/1000)" = "wt",
                                                  "1/4 mile time" = "qsec",
                                                  "V/S" = "vs",
                                                  "Transmission" = "am",
                                                  "Number of forward gears" = "gear",
                                                  "Number of carburetors" = "carb"
                                                )),
                                    
                                    checkboxInput("outliers", "Show BoxPlot's outliers", FALSE)
                                ),
                                
                                mainPanel(
                                    h3(textOutput("caption")),
                                    
                                    tabsetPanel(type = "tabs", 
                                                tabPanel("BoxPlot", plotOutput("mpgBoxPlot")),
                                                tabPanel("Regression model", 
                                                         plotOutput("mpgPlot"),
                                                         verbatimTextOutput("fit")
                                                )
                                    )
                                )
                            )
                        )
               ),
               tabPanel("About the Data Set",
                        
                        h3("Regression Models Course Project (from Coursera)"),
                        helpText("You work for Motor Trend, a magazine about the automobile industry Looking at a data set of a collection of cars, they are interested in exploring the relationship",
                                 "between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions: Is an automatic or manual transmission better for MPG. Quantify the MPG difference between automatic and manual transmissions"),
                        h3("Important"),
                        p("A data frame with 32 observations on 11 variables."),
                        
                        a("https://class.coursera.org/regmods-008")
               ),
               tabPanel("More Data Detail",
                        h2("Motor Trend Car Road Tests"),
                        hr(),
                        h3("Description"),
                        helpText("The data was extracted from the 1974 Motor Trend US magazine,",
                                 " and comprises fuel consumption and 10 aspects of automobile design and performance",
                                 " for 32 automobiles (1973-74 models)."),
                        h3("Format"),
                        p("A data frame with 32 observations on 11 variables."),
                        
                        p("  [, 1]   mpg         Miles/(US) gallon"),
                        p("  [, 2]	 cyl	 Number of cylinders"),
                        p("  [, 3]	 disp	 Displacement (cu.in.)"),
                        p("  [, 4]	 hp	 Gross horsepower"),
                        p("  [, 5]	 drat	 Rear axle ratio"),
                        p("  [, 6]	 wt	 Weight (lb/1000)"),
                        p("  [, 7]	 qsec	 1/4 mile time"),
                        p("  [, 8]	 vs	 V/S"),
                        p("  [, 9]	 am	 Transmission (0 = automatic, 1 = manual)"),
                        p("  [,10]	 gear	 Number of forward gears"),
                        p("  [,11]	 carb	 Number of carburetors"),
                        
                        h3("Source"),
                        
                        p("Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.")
               ),
               tabPanel("Github Details",
                        a("https://github.com/anaghahebbar/PG4"),
                        hr(),
                        h4("This is my first shiny app"),
                        h4("I saved this in my github: AnaghaHebbar")
               )
    )
)

```
MMOZJ4839702665074782935540984118457937174928FAXCVFMFXNZJTGRLRSWUEAGFHPBRIHDFVMXHHQEBYWMERADUVOETZVTNOANWYCEASRXUGTNTFPQTITNDSLRYSQWQNNGLNNWPHMJU"
 [92] "QNHDU0883841069858117870303381434510024935411MHFOPEMFXDNAQVHLFPTBVVMQEJPZWXZKQWKVPMNUAQBOERQWLHNEMOVXPYHZKEELVJEPOZMKMIIQPWXTYMJACDJQRCLLYRHYRULN"
 [93] "GGODS1286977284701543699673254335247238978320QSVSBEVRBOOBDSFUTNZVKKWHNZKDQOZWIVQOLPESKWRUCLCWPLTYBHBCGFSAPFBNKAKNKRNAMAJRPFGHIPEKNMKJUAKHXTWRKBFP"
 [94] "EFGOI2254557112550826284221420444162835549869GXFKZJPKRVLLVDILWWHQORPYGWWFBVABIORKOANXAWMQWKWFMXCYZSZSITBHAKVJWEVIHLZUJXAYZIPADHOXMCOERWEFUFIVDOZY"
 [95] "UKRLN6843341544893183986242266485706244809753VEGGXFQQOEBBZXBJCNGKBMPHOVIFNAIVXNGLWEJDLASROHKMTVTBZDMCBUKRPWASWWKVDEQKGKZFWDOTCOFRVHVDQRLSNOGLLDGX"
 [96] "JDNBR1479753049449215647863839596219272904697YSHJQPTMITAAVLLWDSJLSHEZRGCHPGWFMIYRKEGLIWZFINTOWTUQEWPDYDSPZNCIMVHICTWURHWQMGGEZYNVDAZPXGZXAGMATFYL"
 [97] "GDZLG9676710737276423238739326373530311080902RZTQVMHPREZNGFVFGQLSHUDISAQYFRGTTTEDOHRZTUQZRSLQBXUWPBVCCWYVXQNENMSBPCVHIJYKYVRACQYBZWKIDCEKBFGVGAVQ"
 [98] "PYGBU8108858387995447000281502017150257941861DZJAIYSNFHDDWUBXXBCUDPMVLZGJVLDNTVCOMYSWNOKQQCWZBMAUEFBWMWKYFCSXPUSLEVNTJPHRYOSJUBBJXYPOHUNVOSITCKFZ"
 [99] "IYXJV6039785251221507080191827435263021430033PDZIBYYOYNWOFLARHLQCDBINSBAJDYXEXWYQZVRTWRXSCBVFTKGOMXTORTXLPYDMHLQAESOBJWTCWXRMRQRARJHOXNMHQTMPNRBE"
[100] "KRLSH1507550281867637683594864045226232228999VNYTCARBFCJRDMVIZYSCPWMZXNDTQWIOHJZAZYUXVTYFOTCEITJLFPZUJTGSCVSTCDGWHERDJFEDDSZKEOSLSZEBZSAOFGVGUZDW"

  [1] "ELOGI4252073143005276130185759498112556069432FMMXVJTTTPPCCTDMWHZLETGZKKJVHHJUWJMBOOGUDBZDMGFYAQKOMBWGLCQMLIEFFSYKXFJKXKIQGZSXKQTCVQIOGKBKVGXDLEER"
  [2] "SVALG0827351515950978481845174988325595041231SAJQDLCQJFZHJYIWNCEUIRFDABYJHJPCWNVOXYADJLJRMWEKHNBUBDOJQBRVXVVOGESTTUBWTGHOFJBCSCMOSSPTNPUJECODGSAV"
  [3] "EAKUC9389484548700076338338357667826506732792LSMCIWHBQFIDKMJJAXZVNSXQLLGUKNCPWXDZJVBRVPIGWQUBJOZSKFPGPDYQHGRTCUGNNJQVAPFFQOXTFJYIIXHSJXIKLGQVYWZN"
  [4] "EVDBF0672886898943209977689369782823447491697PKSWSUQIDBWHYWHWFKMECIKTTSIDCNLALIUGZLFLFVPQSWYIHDURKHTCHBJZPDTNQXBAARVLPFKSDSADQSZETZYSXTVMMXOBDDBS"
  [5] "GGBNP9392122196884804659881233792396331831485IGBDIMZKQENMGEZXITPPJWMTUQRKNEXWYWEFMPGQPSRKBNDXMZCQNFQDVLDYSKTZEVZTKDRBRGMBNKOMRONTURRWKKXNXJSDQKSK"
  [6] "JAVMK1198429258722716659180039106840616203119XNOFOVARBAIJSRJWRRQFCVKLTZYDGJDOCVFNGSCGYUNIRJDEGKRAMXCDIUJNNNKTJTEQBIPTBDITKEYMHWYGRAGDECNVRMWLEGFH"
  [7] "RFNNW3666525682273691476463037043974701845130XWEQLIOPEHJNLBASDWSCECUJYYAYJYULMPYPGIWABNGRGLJCAVXBDYWKDBJRIWDYDDVFBBKGFNAFNVBSXIFIUXJVQSXBTRERZMWJ"
  [8] "UZBZD8390203867232984256985544765749733232191RYXCHENYIKSHVCYAWLNYZJGWBLGGNMDXSBWDUQAQQIJNSLSNVIMOUCXDZAKOGDNXHEQCQAMMYIFMVZVGFSVDFSKJHPHBPZGSMSRH"
  [9] "NRBCH1137942534911801431053388986364574941991TSJOLIAOZLQJFYQYOVPCNCKNVIRRQIEIQLPNMSRLBAZUXRPODITKUSAHHNVGDFRDDCFZEEUFXFPKEUYBVVCQDWOICCYQRKIYPGYT"
 [10] "ZSZTF8288030322486256718650961373361287982498GTYWIDHYOFFFPWDNKVYSOLMVODUGSUMXLUWDGSELTEHPGNGLJUDBCRYQZMXTPDFOKZJYQWKXTJGWOKYJXWBJYXQFCJZGNLDQLRAN"
 [11] "GBRIZ8404152196545936853416729833188419576997QUOOBFHVYMLYKSRBVOAVONYMIOBPFMHJXAJMDKWAFFMMTHPRAKMMOYEIRUQMGFWXUGKTFDWTLORKSCJFONILRZIGPVJOVMQLPGSD"
 [12] "UOXLT2710903517730787817065374972479125307521KETFQTRKKNYSUIXFMWZUUHLRPBHKHHRDBDXCXEQIFIXEDLCZPYMUJBIFFHXWFQVMPXPTDONIKRGYJWQKJKFUELCDOOBRVPCOHOCT"
 [13] "EDWJQ1908927119649135875833634572027375894762GZXKMGMIGTMWCXWXFRFGVCZOKAKAVRNOUPVYRBKTQVCTAYXIUVOWDOJJJDZZSCIJXRXFRUJKYHBEUKRJCFBIJSOUTETMCWAKDVWS"
 [14] "JODIL0052076838492445095321529822572022109386EVOXHBWTHLSQKJXECEEGLYAVPBRUPHSFYMRXTUWEHWMDDHHHVLPLLPQMHHTKFTZCFSGTHVNYJQTMCERPXNRMZVSWPWXYIAZLWMLG"
 [15] "IMHGJ6229716732464562846852573652909451653307NKFUTFGOQYHHMKJSNUOTKJZWTHBECRTVFFCWONJTRFLQAFCAVOUWXTICLRWCHCUTMMYLZGHQCPXUBQHTHDGNXHCBHHPNTPTVXTPO"
 [16] "SRZMP9567661363412574501515987270653219018299MDIYOBLRDJUSNKTECYUZLBNVWMJJRTZMYSDKSWUUMRJRQAALCFVXCOEVCOMQDLNFUHUOXMWHQVDQTYPFPVTVQGLGQTAYPJUWZACH"
 [17] "FSJIS0675726625503468028522047287400653815423FMXLZHMVIXGGMSLIHQZQFBESANSNOCCMIVCASRWKAFSEDLNYJERLVKJFWALQCBQZRYYPRBGHSKFOYPIBVFSDSOWEMGQTECKKTLCB"
 [18] "WNWKJ6927511192532903420778888413227613677081FBKZMTFJLQOUGRGAVOHMLLXQAUEZBLSDAIBTCYJZSREBRLRPZKYVQGPMYCQJKWIAHBXMZNQMXVATIPXNYOXBMLXWCCAHQVPKAKVR"
 [19] "XRJYZ7728704968066968739745013959883238036337CLUDYSRURDVAHNOHQULCDQSNBVIEKCLPOBMYYGIFMVWAOEZQLCKBUYPEQVVDRQNZGQQSFWZDKGIQBZLINVZSSLMGPJNBGZVKBLZS"
 [20] "TQCSG9775347835054466319452086417814408039128FDAVJONYTITQWJFPKPRYYFGEFJSMXDRSXFUJJALOMGZPKOHSKEVQJFLMBOSXIKGAJAHDKFUHIYFMXUSQYVLDZLMABBEYFYFMFYBV"
 [21] "ZHWCD9916803655867733127596247246339581691143YHYLPNBQIICSHMCZKJYTCQQVHLHHWUPJDBTIZQJNOTDXPMBEBAVZWRSAFTXCEXQNDUROKEXTNWQSVNQMZHLJMQCBZHLBEQLXJOVC"
 [22] "EGXGU8813957536316988717192935624230040591882ANDNKPJDIGERQSNAKXAQKCDXGIGHFQUTYSTUPNNAOEKWXAACYTJUHUQPDGIHFUMNUVSRJMJTNFTGQVJLLZDVAJZHFWXWRAJARWET"
 [23] "DVCTG2914653877329621984420428519854236898738JEDUUKQZMDEGORJUKLZQOCRTHBYJBCTICKBUJRWLGOXUTUHTGLCYJRMZMQOEYSNPWWPGPSXCFAOWIPMGMJQLDNGLEOTMSZTUZAOD"
 [24] "MMIKA5773059573329070754079713304918545786397USDCVPYWYKACZWVTGGUJIZCHEJRUBTUENEIHFODIDJVUHHKWAPPZTDNTLRPKLSBDGTPNHFKSZPHOZSQRTFZEJLZLZMFQISXVYYAC"
 [25] "DOOHF4066388281541427790733430359730930753184HOGJZYDNUACEWEHOTIZBRMKOSTFYBLMUCEIIIDJADZSYMEVZHQLXSPDQTRXPRBOSMDROVWFDQCDMJLKMPQOOTCOPSCVMEOMCTXBG"
 [26] "BIMPG9204578723012106668275488499545573256663FWNJRSHNBDAAFJQILAYYXCWOXKPAIKTNAIQGRQVODCEDWCYYJCVYVCHMHNAARHDSWELMFTCMOQYBISHOFIILVDBJNHCWKJNEYZCU"
 [27] "UAYWU4139043900774378579963380336479873956002QBLLMBHGVUJHWGEHJSYPTYDVRMBQIDGSLNUWPWHRBFIEEXEINRWQFKXZZZPJHGEFDCSZSRKMHXUVDZUELJEZXZGHHAYKNGQOAFUD"
 [28] "ZAYUO5110227880823549882632014674185118355161JPIAYDTAGXGPFDCUSIDNMTGAAMAKMAZDPZYIOEWYXYNODNRRTDYIUMGUJIKFYVLZVIBJCPZNWPGRCOWJVOPSFMMOKLZDPKVZJUKZ"
 [29] "UWQTS9642994031500327253444085790555022187760IYGBCBBRPYVTRJPZKLZGWKLPRCXFBHWINWFTUCPHTMWNAEUBZXJAUQYOFQMLNTCZIJLZGMPLSFFQXKNYSQHTIGTMEZADNXJMMFFH"
 [30] "LTJTC3293583384675189287690712583888451545474PGXBAMBDYUVOSWQBIJCAWSAHTBAMAHJWFYDQRESZNVUILGYJHZOEHZRFWHFNKBKRGTRMZBSCFEFJGTXJVKXCWCAUSMCYACIHVLSY"
 [31] "SCBLC5474200024119623492057395109530420626306SWEPPPCYAVFMOFCKZWONMEDXSKYUOIWDRGUVWFBHTGJIQFRGGZRUORCCUAIIQAQXULBJXQHOWYLQJXDZUXPDMTRSDCOQNWAZATLM"
 [32] "SSVUN5650156979128647051236397395794347859306QORWENVZEWCVHJOXAEJJTQDVICMORAPTCURRDMBKPDPZOIOGSJPTQLXGBAMVTXIRWCVSRZKWGZEHMFTNEVDKIGLBISEXUSCXVMOU"
 [33] "YJAKD5087362892846695303098917553324059472246RVRWLVMKLMKIHIOUXHUBZEFSCZWHFZRMSMQLAKSFEGSBQETPVHSKBQBFRMXPXWVKTCASZMUDFSYSSDPJBJOKHOLIHTQNWWOLCJKZ"
 [34] "BYEWD7814310155569310562284226135655706355347GDJTERSZNCGVXLGAUFOXKAFVCABFZSPSRIHNDGFFDXWNPAYCNRPWZTXUZVGHLIJMLTNCSDBRDHBYUQUJVLFZBEPKHTFSSVNTPIAN"
 [35] "XQYOP4592982274782159520412055014447217655253RVDDJGWUATHOIUNSGLDITLWHMVARTKCBTLCPEDEPECYKIJCEZNXSUEFBIPURFGFVPEZSKBZDCMQSHPXSTGSFZVEJANXMHZPZWFSI"
 [36] "ZOSBD2497891188326321394900741416703751745136LVGDRDVRFITKTYRVUHGBJUIRXZGBLKZXATMJLHWWXYSQGCIKIANKCSGSJJNHHAPHPZMALWZCNOCDMLIDRUKXQYDWQBZFSOEGAPOK"
 [37] "MOWSO5155373427526220319286494216022130567380FVGXCFWKLDLSCCJCOQTHEDRFNTOHGHKUJKPJBUTHKXOKLDCCJBNDCGMDISPWYVCXHJNVWITASKQDWTIMWXIUOJBFBABVYWQPXXGI"
 [38] "HHTNJ9719141244745502330928438750049831565786ETZJWHDKPXUKHVPNQPFELCOAOUESRLMFJVESTFRTZSQRRBAUEBQWOFOFYIOZEJEYBDDSYXZXNKVIUIVEFEWLCBIMRXWRLHQYKITJ"
 [39] "RAAFG9223625293456529931086926990579927215190AYASESDSTBGKECMEGCXBRBCZKKCDCPAMGVRJTDEFBXLHOLVGFUTQFMQWKLUVJVGTOGWVHFVAQXBRKASKVPZOTSBHMMWYUJDNPVOS"
 [40] "TPLYR9898570364672336191878244023242146147518GRXFFNSDAOSBJYNLDIJXHGKDAKSXPARPMMLDGSCOCBFBXGYUOLGHZXOVZSUZMMRYGLYBYDLQKSCSVKXXFOAOFWKWBEEVENFNECFI"
 [41] "PHFPJ0313241823152017758497874252504196400627ESLLYDBGGADPGLXJNOKNGGUMACGRBSWLOMBUJMCDDEWYXNKGFNRYCRPIOGAKVITIVVPYKXDJWHOLUZGGNNRKPBJBWKLITRCOBCOJ"
 [42] "ZSPJV6318086944217908709436735302240858207817DWNWQXLJMTJSGVWGUSGEOEGQJOOMBDDXUWDYUQKJRDTAJLHNHDYWSCWUWJRWLJQWUGYARXNCCRLVKRVNIBFGDGCKTGBUSSERDOZL"
 [43] "XBLQV6306794998653023172777051669975661252570OOSBUOBHZGSFSJBUWJFVPFLUJDQTUGEGWMYWBQPQYRKYJYZSXCXZCCNITBZICYEZCNOWHNOKQZPANQNFEANEQBNTVFSLQIJBXURM"
 [44] "XNHVB8817358680371991456226781391710730274499SDCRZKDXLNPUAADKGZFQWJVBMBWRMICTVUFJZMMDLPYKISYWWMTQHWPWMKTKOCZOIXDXYQNFYGAJPLGHUIAVGKHQSYJNRQPRMEVG"
 [45] "WLVBH3080903326292413500674272473139268900801RNTMSDDBGRYRGUNRSLZLHCKWFMVEHVJPZUDDFJPLCNLGYRFFJUIRUZDCZPJSJVMAOLNXGKDTOVFTGYVZKBAWXJVQZXWFRULKVOQH"
 [46] "PFOTN0813585053614776324399631073535053436599ILPJYTIOHLVKYOITSJHEMZUBKRLKMXPJCOITYYFGPOAZXWJAGZVJPPDNFSVDGIAAEXDIYTOJUBOCRTJUPLBOHNJIAPGHPHDZLDYQ"
 [47] "GVNAH6471583809892377755945917575030505120080ZPIFOOSQFWPFIUCDKEAZDCCHEXURQXAVNPDQGQJQLWFUHXLVSDVPTPGDSANNMHMOZNNBCCRSNQNIBBSSATGTIIVFLMDGNZHAVHJF"
 [48] "AHBNH5500071386396381180423258240214084697840PYNMKMYYMPCAHQRZTLPTKQKWFKAJARSFUVLSVBPLJGBONCZAUAIXCEOPQEICGPXUFTDHPYSGRSVQAYFKEMRCQAKWEZGDKDKUHULX"
 [49] "ZVVQY7694514046661446331858023109440424195791LUDRSDUBXLEUBBMNZMGBMXKZNLLJCWNDFDCDTQQCNHDDVTYBZGCJXCXCSXRRYKWFMQKXZGHSHEICTZAOYKLQEVMZMPOLZPGMAKDG"
 [50] "QVOJY8649621576251581443522097289755842118584ZZTPNQGUYAJCHXQNISNRHZQKGFRDEQXCJJUHWZDQROTHOBUASKLZVKILMOATHXYYHDMCRHQOXQXBZIOKYXYGUZHGZHDEILOBMCUT"
 [51] "WQBRC4252073143005276130185759498112556069432FMMXVJTTTPPCCTDMWHZLETGZKKJVHHJUWJMBOOGUDBZDMGFYAQKOMBWGLCQMLIEFFSYKXFJKXKIQGZSXKQTCVQIOGKBKVGXDLEER"
 [52] "SVIUH0827351515950978481845174988325595041231SAJQDLCQJFZHJYIWNCEUIRFDABYJHJPCWNVOXYADJLJRMWEKHNBUBDOJQBRVXVVOGESTTUBWTGHOFJBCSCMOSSPTNPUJECODGSAV"
 [53] "FHDIW9389484548700076338338357667826506732792LSMCIWHBQFIDKMJJAXZVNSXQLLGUKNCPWXDZJVBRVPIGWQUBJOZSKFPGPDYQHGRTCUGNNJQVAPFFQOXTFJYIIXHSJXIKLGQVYWZN"
 [54] "YEORS0672886898943209977689369782823447491697PKSWSUQIDBWHYWHWFKMECIKTTSIDCNLALIUGZLFLFVPQSWYIHDURKHTCHBJZPDTNQXBAARVLPFKSDSADQSZETZYSXTVMMXOBDDBS"
 [55] "KNPMM9392122196884804659881233792396331831485IGBDIMZKQENMGEZXITPPJWMTUQRKNEXWYWEFMPGQPSRKBNDXMZCQNFQDVLDYSKTZEVZTKDRBRGMBNKOMRONTURRWKKXNXJSDQKSK"
 [56] "IHXEI1198429258722716659180039106840616203119XNOFOVARBAIJSRJWRRQFCVKLTZYDGJDOCVFNGSCGYUNIRJDEGKRAMXCDIUJNNNKTJTEQBIPTBDITKEYMHWYGRAGDECNVRMWLEGFH"
 [57] "MHNNM3666525682273691476463037043974701845130XWEQLIOPEHJNLBASDWSCECUJYYAYJYULMPYPGIWABNGRGLJCAVXBDYWKDBJRIWDYDDVFBBKGFNAFNVBSXIFIUXJVQSXBTRERZMWJ"
 [58] "OSSPJ8390203867232984256985544765749733232191RYXCHENYIKSHVCYAWLNYZJGWBLGGNMDXSBWDUQAQQIJNSLSNVIMOUCXDZAKOGDNXHEQCQAMMYIFMVZVGFSVDFSKJHPHBPZGSMSRH"
 [59] "QNMAU1137942534911801431053388986364574941991TSJOLIAOZLQJFYQYOVPCNCKNVIRRQIEIQLPNMSRLBAZUXRPODITKUSAHHNVGDFRDDCFZEEUFXFPKEUYBVVCQDWOICCYQRKIYPGYT"
 [60] "FKBHM8288030322486256718650961373361287982498GTYWIDHYOFFFPWDNKVYSOLMVODUGSUMXLUWDGSELTEHPGNGLJUDBCRYQZMXTPDFOKZJYQWKXTJGWOKYJXWBJYXQFCJZGNLDQLRAN"
 [61] "FQPYW8404152196545936853416729833188419576997QUOOBFHVYMLYKSRBVOAVONYMIOBPFMHJXAJMDKWAFFMMTHPRAKMMOYEIRUQMGFWXUGKTFDWTLORKSCJFONILRZIGPVJOVMQLPGSD"
 [62] "BNTTO2710903517730787817065374972479125307521KETFQTRKKNYSUIXFMWZUUHLRPBHKHHRDBDXCXEQIFIXEDLCZPYMUJBIFFHXWFQVMPXPTDONIKRGYJWQKJKFUELCDOOBRVPCOHOCT"
 [63] "MHWXJ1908927119649135875833634572027375894762GZXKMGMIGTMWCXWXFRFGVCZOKAKAVRNOUPVYRBKTQVCTAYXIUVOWDOJJJDZZSCIJXRXFRUJKYHBEUKRJCFBIJSOUTETMCWAKDVWS"
 [64] "ZQMJI0052076838492445095321529822572022109386EVOXHBWTHLSQKJXECEEGLYAVPBRUPHSFYMRXTUWEHWMDDHHHVLPLLPQMHHTKFTZCFSGTHVNYJQTMCERPXNRMZVSWPWXYIAZLWMLG"
 [65] "PWFDF6229716732464562846852573652909451653307NKFUTFGOQYHHMKJSNUOTKJZWTHBECRTVFFCWONJTRFLQAFCAVOUWXTICLRWCHCUTMMYLZGHQCPXUBQHTHDGNXHCBHHPNTPTVXTPO"
 [66] "SIPBL9567661363412574501515987270653219018299MDIYOBLRDJUSNKTECYUZLBNVWMJJRTZMYSDKSWUUMRJRQAALCFVXCOEVCOMQDLNFUHUOXMWHQVDQTYPFPVTVQGLGQTAYPJUWZACH"
 [67] "FOZOU0675726625503468028522047287400653815423FMXLZHMVIXGGMSLIHQZQFBESANSNOCCMIVCASRWKAFSEDLNYJERLVKJFWALQCBQZRYYPRBGHSKFOYPIBVFSDSOWEMGQTECKKTLCB"
 [68] "ADXSP6927511192532903420778888413227613677081FBKZMTFJLQOUGRGAVOHMLLXQAUEZBLSDAIBTCYJZSREBRLRPZKYVQGPMYCQJKWIAHBXMZNQMXVATIPXNYOXBMLXWCCAHQVPKAKVR"
 [69] "IHAFH7728704968066968739745013959883238036337CLUDYSRURDVAHNOHQULCDQSNBVIEKCLPOBMYYGIFMVWAOEZQLCKBUYPEQVVDRQNZGQQSFWZDKGIQBZLINVZSSLMGPJNBGZVKBLZS"
 [70] "KFFQC9775347835054466319452086417814408039128FDAVJONYTITQWJFPKPRYYFGEFJSMXDRSXFUJJALOMGZPKOHSKEVQJFLMBOSXIKGAJAHDKFUHIYFMXUSQYVLDZLMABBEYFYFMFYBV"
 [71] "IAFLC9916803655867733127596247246339581691143YHYLPNBQIICSHMCZKJYTCQQVHLHHWUPJDBTIZQJNOTDXPMBEBAVZWRSAFTXCEXQNDUROKEXTNWQSVNQMZHLJMQCBZHLBEQLXJOVC"
 [72] "IGPKP8813957536316988717192935624230040591882ANDNKPJDIGERQSNAKXAQKCDXGIGHFQUTYSTUPNNAOEKWXAACYTJUHUQPDGIHFUMNUVSRJMJTNFTGQVJLLZDVAJZHFWXWRAJARWET"
 [73] "WOOTQ2914653877329621984420428519854236898738JEDUUKQZMDEGORJUKLZQOCRTHBYJBCTICKBUJRWLGOXUTUHTGLCYJRMZMQOEYSNPWWPGPSXCFAOWIPMGMJQLDNGLEOTMSZTUZAOD"
 [74] "GADFO5773059573329070754079713304918545786397USDCVPYWYKACZWVTGGUJIZCHEJRUBTUENEIHFODIDJVUHHKWAPPZTDNTLRPKLSBDGTPNHFKSZPHOZSQRTFZEJLZLZMFQISXVYYAC"
 [75] "ZLHXG4066388281541427790733430359730930753184HOGJZYDNUACEWEHOTIZBRMKOSTFYBLMUCEIIIDJADZSYMEVZHQLXSPDQTRXPRBOSMDROVWFDQCDMJLKMPQOOTCOPSCVMEOMCTXBG"
 [76] "ZUNDB9204578723012106668275488499545573256663FWNJRSHNBDAAFJQILAYYXCWOXKPAIKTNAIQGRQVODCEDWCYYJCVYVCHMHNAARHDSWELMFTCMOQYBISHOFIILVDBJNHCWKJNEYZCU"
 [77] "XZGKR4139043900774378579963380336479873956002QBLLMBHGVUJHWGEHJSYPTYDVRMBQIDGSLNUWPWHRBFIEEXEINRWQFKXZZZPJHGEFDCSZSRKMHXUVDZUELJEZXZGHHAYKNGQOAFUD"
 [78] "BTHOY5110227880823549882632014674185118355161JPIAYDTAGXGPFDCUSIDNMTGAAMAKMAZDPZYIOEWYXYNODNRRTDYIUMGUJIKFYVLZVIBJCPZNWPGRCOWJVOPSFMMOKLZDPKVZJUKZ"
 [79] "QMEDZ9642994031500327253444085790555022187760IYGBCBBRPYVTRJPZKLZGWKLPRCXFBHWINWFTUCPHTMWNAEUBZXJAUQYOFQMLNTCZIJLZGMPLSFFQXKNYSQHTIGTMEZADNXJMMFFH"
 [80] "QEDWW3293583384675189287690712583888451545474PGXBAMBDYUVOSWQBIJCAWSAHTBAMAHJWFYDQRESZNVUILGYJHZOEHZRFWHFNKBKRGTRMZBSCFEFJGTXJVKXCWCAUSMCYACIHVLSY"
 [81] "ZMWVG5474200024119623492057395109530420626306SWEPPPCYAVFMOFCKZWONMEDXSKYUOIWDRGUVWFBHTGJIQFRGGZRUORCCUAIIQAQXULBJXQHOWYLQJXDZUXPDMTRSDCOQNWAZATLM"
 [82] "WWCYP5650156979128647051236397395794347859306QORWENVZEWCVHJOXAEJJTQDVICMORAPTCURRDMBKPDPZOIOGSJPTQLXGBAMVTXIRWCVSRZKWGZEHMFTNEVDKIGLBISEXUSCXVMOU"
 [83] "XZCLG5087362892846695303098917553324059472246RVRWLVMKLMKIHIOUXHUBZEFSCZWHFZRMSMQLAKSFEGSBQETPVHSKBQBFRMXPXWVKTCASZMUDFSYSSDPJBJOKHOLIHTQNWWOLCJKZ"
 [84] "PVTOK7814310155569310562284226135655706355347GDJTERSZNCGVXLGAUFOXKAFVCABFZSPSRIHNDGFFDXWNPAYCNRPWZTXUZVGHLIJMLTNCSDBRDHBYUQUJVLFZBEPKHTFSSVNTPIAN"
 [85] "IVXEJ4592982274782159520412055014447217655253RVDDJGWUATHOIUNSGLDITLWHMVARTKCBTLCPEDEPECYKIJCEZNXSUEFBIPURFGFVPEZSKBZDCMQSHPXSTGSFZVEJANXMHZPZWFSI"
 [86] "PKATY2497891188326321394900741416703751745136LVGDRDVRFITKTYRVUHGBJUIRXZGBLKZXATMJLHWWXYSQGCIKIANKCSGSJJNHHAPHPZMALWZCNOCDMLIDRUKXQYDWQBZFSOEGAPOK"
 [87] "EBKTR5155373427526220319286494216022130567380FVGXCFWKLDLSCCJCOQTHEDRFNTOHGHKUJKPJBUTHKXOKLDCCJBNDCGMDISPWYVCXHJNVWITASKQDWTIMWXIUOJBFBABVYWQPXXGI"
 [88] "RWXMX9719141244745502330928438750049831565786ETZJWHDKPXUKHVPNQPFELCOAOUESRLMFJVESTFRTZSQRRBAUEBQWOFOFYIOZEJEYBDDSYXZXNKVIUIVEFEWLCBIMRXWRLHQYKITJ"
 [89] "VUSFL9223625293456529931086926990579927215190AYASESDSTBGKECMEGCXBRBCZKKCDCPAMGVRJTDEFBXLHOLVGFUTQFMQWKLUVJVGTOGWVHFVAQXBRKASKVPZOTSBHMMWYUJDNPVOS"
 [90] "INXCX9898570364672336191878244023242146147518GRXFFNSDAOSBJYNLDIJXHGKDAKSXPARPMMLDGSCOCBFBXGYUOLGHZXOVZSUZMMRYGLYBYDLQKSCSVKXXFOAOFWKWBEEVENFNECFI"
 [91] "ZMLIZ0313241823152017758497874252504196400627ESLLYDBGGADPGLXJNOKNGGUMACGRBSWLOMBUJMCDDEWYXNKGFNRYCRPIOGAKVITIVVPYKXDJWHOLUZGGNNRKPBJBWKLITRCOBCOJ"
 [92] "YFAXU6318086944217908709436735302240858207817DWNWQXLJMTJSGVWGUSGEOEGQJOOMBDDXUWDYUQKJRDTAJLHNHDYWSCWUWJRWLJQWUGYARXNCCRLVKRVNIBFGDGCKTGBUSSERDOZL"
 [93] "BSJOM6306794998653023172777051669975661252570OOSBUOBHZGSFSJBUWJFVPFLUJDQTUGEGWMYWBQPQYRKYJYZSXCXZCCNITBZICYEZCNOWHNOKQZPANQNFEANEQBNTVFSLQIJBXURM"
 [94] "REQXG8817358680371991456226781391710730274499SDCRZKDXLNPUAADKGZFQWJVBMBWRMICTVUFJZMMDLPYKISYWWMTQHWPWMKTKOCZOIXDXYQNFYGAJPLGHUIAVGKHQSYJNRQPRMEVG"
 [95] "UYPIG3080903326292413500674272473139268900801RNTMSDDBGRYRGUNRSLZLHCKWFMVEHVJPZUDDFJPLCNLGYRFFJUIRUZDCZPJSJVMAOLNXGKDTOVFTGYVZKBAWXJVQZXWFRULKVOQH"
 [96] "IJAGD0813585053614776324399631073535053436599ILPJYTIOHLVKYOITSJHEMZUBKRLKMXPJCOITYYFGPOAZXWJAGZVJPPDNFSVDGIAAEXDIYTOJUBOCRTJUPLBOHNJIAPGHPHDZLDYQ"
 [97] "FJQSR6471583809892377755945917575030505120080ZPIFOOSQFWPFIUCDKEAZDCCHEXURQXAVNPDQGQJQLWFUHXLVSDVPTPGDSANNMHMOZNNBCCRSNQNIBBSSATGTIIVFLMDGNZHAVHJF"
 [98] "MDAGM5500071386396381180423258240214084697840PYNMKMYYMPCAHQRZTLPTKQKWFKAJARSFUVLSVBPLJGBONCZAUAIXCEOPQEICGPXUFTDHPYSGRSVQAYFKEMRCQAKWEZGDKDKUHULX"
 [99] "KEKYX7694514046661446331858023109440424195791LUDRSDUBXLEUBBMNZMGBMXKZNLLJCWNDFDCDTQQCNHDDVTYBZGCJXCXCSXRRYKWFMQKXZGHSHEICTZAOYKLQEVMZMPOLZPGMAKDG"
[100] "LILQM8649621576251581443522097289755842118584ZZTPNQGUYAJCHXQNISNRHZQKGFRDEQXCJJUHWZDQROTHOBUASKLZVKILMOATHXYYHDMCRHQOXQXBZIOKYXYGUZHGZHDEILOBMCUT"

  [1] "GYXKD0600915984568662748323102309094538493202SHJZSJBQSBDMQTFCBESZBEKUWBFUNMMVCVKFNWVYIBUDDERPDYHNSDIEKKWAROSGSDPCCTFEZGQZJSHAFEXJSUBJIBAJSSNTOFNY"
  [2] "OCKNJ2871208543737604239882163609993878660253GEOYFQTQCDPWCQYIUYLUBRQKWPOGETTRPRFFGRMPPLAXRHJFITUBYUJIANVVLHXMAXASUMXSOPWFYFMNKBTRBDJBENRKQABUVDIN"
  [3] "CGTXO0463406752401817577410199454642844369572GBHZKYGZVDEOFWKNDZYWEQLDXCOXPGNUJKUZBWNBIAPTDKBWYNHCFGRJOQCSGSNFNQCFIKSVQMBOPZWOFBVYPAKWMEAIPDJLTLEF"
  [4] "VLMNA2378246902596608274227296227251733087093GATZPMNREXAMPOPOEIRLXDNIEQEIUTPQWROBJWKBWDOQMFXKNRRCBPDABKDZNSMTVYXMWRBIRYIJXBMXFAADEKABFQAURYCUGLFC"
  [5] "KUVAO1377283321831698169028947658602987161863HSXPTOMZLSNLUREAQEUHQJIENQMMGBIOABHSVHJIZRLTZEHXTZNPTZZWVGXNGGCJCWBJEZYHGFSBAABCVMJFVVHVJQPAJLGFIZLQ"
  [6] "UGQIB6564052169738907816093406549672819255229HXKTWOCDTXWTXJRBIZRNHYELGQZQJZZOUHWCRMKVYSIZFLFZOOUFPDATCPRAFTQFPVCXNKKXYTYBXDUPCWNDQXJZZEUPUPXFDKNZ"
  [7] "WIDIN1716972391548314590560678931279191684464NPDRDDGYOQCGTZOORHLGXUQKZEHUYQIGRIACDLTRNEPVICFKPZPLWTJRZDXCTKKCZVMJTSOSMZWUKUGPWIPVWOMUAQFGIJRZNHVI"
  [8] "XXWFR7591612308360380548289158585512624395768ZOURGCUHHSWMKJFPMVLZFKSJTXOJCQOAVFSDMIIUTJUFQHGZDBJHOHRPMSWKCQITVOJNQYITDKYDFSILHVSFHKEYOPBNHUEIOJUW"
  [9] "BRNLG1591970396796665709400813646691199384041LBMLVYFWBKJJGKKBBKGAHYYUINAVETRJSLWKXITAZONZHRJFHDEIIKKNSTUPJOEQWMTUHQCWJVOYSSZPLYYLDVXKORRKUONJIWKE"
 [10] "MSWKQ5021361263104822815484279275721209983552BKEEIERITYWVYKMVYKBXEUHHBIVSHTGCIBQDXZWJUWZUSKLBSEJQQXOHZEYFELZLXYYCMTQEBMJIRXXFLCKGSCGDXEPVLMFMOYXW"
 [11] "KUVHP8781091275141653825005044516923425173101ILRPLLXKIFGIVQWKUCZRGJUDXYKVMXNIBZULEMRKASEMZKNAEZHNBWIJYXEVEIFZBNWJNANOLJLHCDORFEKVUPAWOCAXODLEEUSU"
 [12] "DLIWF5888068838388896375263691739542413458914SNQJDCCSLLDSKGGQSUGZJUYZWMGLGMQOEBOXMTLIOOZVQFNOBDNCSGVHCPHJBCODMXGYWFWXKWRYSRXYKSNDJKVRPJIDUOUXYLEW"
 [13] "LTCVN5462447058520394658714436020783253143991YKZOJLTKWORRKXJVUQHGIOIGVGFIKTLIBFDNBKBSIZMDGLOJBGHBHEVSHZXWKGXAXXJVHKJLJOZWIQLYWYBHSRYEUTCHNMIGRTEM"
 [14] "PITUT7801235878012262734478816993153923594205QJIUCKSLKSWXRBGUSYRCZTLWQUMNAFNKHRZEBZSFLXSCSLADQKAWUGPLDXDGPEPHNCVXLUQFNWPWUXKGZODSWOBLZVTXMLARYGII"
 [15] "TMWBP8392034899044198890891565218785068021301SSWGIBDPRGNLVSTTZEMYBMTTFAJBUXTCMYMXCVCFUKMFZTRBUFYOCAIBFAGPHXJTMBRJLUEKKJRPNOESILOZNBCCGWSIQHXEZDUW"
 [16] "JSZPS1272277395746494794548249998816566003059EOWLFUOPXZTQGRAUZWWWNQDNNOTSLUEPGPXEYUPGHESPSRHBWTQXFRCPBYXMBEXAZDHMQWMBERJBXZOKKIWIDZQFPUZTZJCSUYRY"
 [17] "JXPKU0233651799493571118773931029363738564270RAGCZOXRGLJNKXAIEVJUXXZJUFAIXZCJFGBZHZZVCEFTQSBIBIESBAEKMPISDFQCGJLEYTYIINROPWHRIKFSXQBVPNTBGRCGRSOA"
 [18] "GGCNJ1208567586948073779156240698918844377823DUMHUXAXKTKUDMCJBWULIALQUPECPUSKNGNKMUQMTBIPRAANRTARPBXYVEOFDHMWWXCHUKZKEPCTPPGARFEYXYMBRCHNLFMTUDTQ"
 [19] "YOFVL3407753851378753276695923439588018884429QQBSPZTKRFYHXJDRCWQDFHYUFLVYTVQTBNRYMIHWOENLNCFPKDVLQUBPYSWSPINZVZROSTAVRNPCQKNBMSATJLVSJCTOCVAZECUB"
 [20] "ZZQYH9518095826890092588380236834040122670899KRGYLLSFUSQKRJJUFQMEWOCJBPJBARGRIKFAMYBTAZQUXSUNBCOGCBDMCDQTDSLABXCYARYGWFBNERDIVPDMGQKUGUBUAJSJJLFA"
 [21] "GYSVH9039353981604290613068188497325075905762CRBGBRTGSYAIITYPMSPYLGMQIEUDKZDIEDGHCOCXCBTBRVXETICEYOGOGTRUALHXVNSTSWTBJUFECDEICCCAHGZZAIKACNTDYSMZ"
 [22] "TDDGO2541665511022397554586193000504906014306FFPVZJYSFGFRWTWEBZXERXOWAFMDKHBZRZYMGMXHWBGUCAQPVWYZESJOCQIMAFLNHNHYHELLCVFNXAZDFUFXIACUEYEJCYDESNYF"
 [23] "FYJEC8691729965318809359172418725969366280077DSRNZHTXBLGFBAFAZBEFDAZWYNICUQVUUGEPKJFYXAORTWWFGMEEGSHFKKNJBGMYHCQJKERSMMDDBOKGRMEGPKTLXJYHGTWAYVVI"
 [24] "PXPXQ0752679863398205999633000579342926986322HRDLNZNIERWGJNVHJGIUWBQRRBLIGJWCLRNZFVESUPFRQZXGYISYGYOSQCNWQHOCIOYUJFMOXPBDCIGWSDCAAKZBOIYXQHIEUPUF"
 [25] "TMBJF5263704595890281436545642862300178661552YMZEQKIKFONNNFYTSFCIQDHTSPRRGVCBOXNCUUYAIHGKDRBTQYYZOKFEOAPHUQOPNOCMHWRHSPEBFNBIGJCPMYOIIELNHBRBGJEI"
 [26] "BUIDD9279481762899564775623714880380036195115RXMVNEELFZODMCRMLIVMQRYJUDDDFRTXXYAFCTZWTTGWKJNVUGSXEDISVANBKPYLBOTKCJNPGWUHZUKMZJUPXBHOTJOKBMGNDLPC"
 [27] "RRRFZ6486857901077210743837784936885338063963DPRFSQWZSMXNXTOLNRTDJCIBPBQZCDFFDDYHUMVDSBNHZFRKHITUDGHOYXVXKTLPEPBZUHLPPTDPCXHVXJIPBHADVTSCPAPZCDXO"
 [28] "LSBKW3878336446071537219582968322363472092403RAJHLSFNKADUPTGYRQWDWRLTWGMIDLPZJBLNBHGTBVEITQYQQDIKLYDMLZBHTOAIFABQGYWHPUANXXZEJDTWUBOBZTKRPEXQTRIH"
 [29] "UUVIR9345538605961656977056446516047916015923QWHPVGBHRJCDIOTPAUSVJTODXRHGROXGUILPOJQHCLAAMHPLMQJEEHUIRAHCXCJKUKGXKEKSROZPZUEOBEAKZSZKZSMMLSHWLHIF"
 [30] "QAKLX5305971422048144681889610214375987253437EGJRGILIKXTKMKYEUFTLIIQFFWLYCRNQTFJBPCXGSMXDAVLELKLLJPNGIFLHCYRVISYUWOYEBUSELXGXVSDUKJJYUSLQYBXJGXMS"
 [31] "IJHAG0836628191244384108601230895311931050648DZDPNTZQCGDBYUDHNOYTUABKMSRESPRGQZCWTOWXZXDGXQOJADEWXNOJHFOGTCNXDKLPQNFDNTZJJBDDOHXTFPJKASWFXAKJFKHY"
 [32] "ZYYSZ0092904684587010560783743178697923627488LSMCLHFRWHSIRDTIXFIPQWYGFTYUWXWEUHZYHRNVVUPBLYMKUUEWQDWGKWGTTDFMRKEHYTHFHSYZCOVRTFXZUCSSIWGOAOKXKCQZ"
 [33] "OAHZC4066382062934597965904679170187555659437WKGJITHBHMKIVTLJRXEVLHTKWKOCLBSUOYHRPMQQEAEHETEYHDGBUJVSQINLXKMIXCHHPULYAHOYSDFQNOJFGTPGMGHLLBXCGHPS"
 [34] "RZNUE3289231997193221343040676370537892080990KPFEFWJPOCGILIAPRXEJWWGNIGSSOXVGJVHYJKHDFZMROTFSMBOXYPJBVGCRDTONSIXOZMOWDQVMFKPASLBBIOAKZKGVIHFVEUKQ"
 [35] "DDDZU0543258616222363553297893261061338958213PDJRLLOPGTMRTXWQINTGYWEJCYUQGQAPLRQTINLWLUCKIJRKSZWJIRGDHUKONQQZNDBCKJHQEEULHYUTHCXVTBEICEXSBDHNOVEZ"
 [36] "FEIMR7650790706194283694741181247885277170389EJYXTCJMJHWUSRJUDWMAHBIOXMVEVPTZXXVOFEIUABMAALWQBZSPKVKMNTDDHNIGFLUYNXJEAQVIJFCEUEOHRGDZQAQWMUJXRZJW"
 [37] "WQAOR8793839024042710216898640685126984776999IGRIQGPGIFTXTWIKAUJKFSCDYZDZHUEPHYRHGLAFAGESAJHJGTRZSXPMKJFXFWOPEHOQXWMWYYBAAVDVQWCBGAAIMHOKCPOUPZWT"
 [38] "IRMLW0070663785594559430227841464742779214107YZDXTYPAKKZECYAZHOBUYBKPWRBYDFKANZQUFSGHIWNQCUAPPKOORNHNCNTLPNMWCSWSBTIHEDPIWFLRDFLNPIOALJTWSTWCOYCU"
 [39] "LITDJ9252160166184756823838963402478484121746ASBLIMTIXPPTPIPRARMSEVKCROEWEBVQZBHMGVMKKEGNQQMMAZWXKVQHNZTJWTOSHSOTOJIJDSGBJEGVTDQUEXOIFSVCLNJTRCFR"
 [40] "KHUQG2862923129611624482317440654993364343478XCYHYTOCSVRGBBBQWOOPNFCOXRGJIHTOXKXNETUUHRQDVXCMODXWKCEGXQIKAFCKUGNVQTZWQDAXDEITBRZXOMMERGYDYMPGYFZJ"
 [41] "OOTOT1463992807395034459777110617798351515477ZKILJWGURULNWHJPULBTNKTTKJVJANEQDXWRTDXEZLIWEKMGVFWXDTDBSVUSGVCPPIYJICDTSCLJHVHKWXTGLTUQRBVIOBZZHGLJ"
 [42] "XTLBP5221044260168865120706648077880402165314XGCJOAQFKAUKYVXWLGQLPPZIEGUGLKNZEYVCWHYKLHEPYSWUSNEAMAUMOFXVLDLPBUKQCLBWDLPZICPQKJQNPRLHEFPFTIUFIWGT"
 [43] "NPSIN1883599645090572177365689502697184704441YDAVVJYUWWQMYDETJIJENCNYVBARCJYRHDZPBXWESXZBPTOLPGZNWTUSMZOAQLFLFNVLQVJDLIQUOQBYINMRXQITQQVFUKSVBORW"
 [44] "YMYJL0272663513510202543783813275994992774827HPEEMHDAYLOEFPKSRCSLMSVSHLCMTNTKWPQYDIWACANOWECKCHTZZXYMWASVZACTTPJIOEVANMRUPEKMYSJDZXXDJUEDAXBWTFRF"
 [45] "UMBBY1680500943047495168171842307761975528645XGBDFDJCSUKYURRMYECPZBYYWGBYZBFNWFBQOHAWTHCUQWTTIAZDHJLNQLOHYGEHNNNLAVAEPQOYJHVXMYFKHANPJUJSCFQRMQBV"
 [46] "CMJGS6816657804978054362384017418019265095410ZBULNUXLUOTWBKGTZCIXCMSCBXGMXIGKHRNPBATOAZVPKIGENVMDSATXWMWDENOGRCXDRPMGKPIJXLGLFHPIONHXSHXLACRZIRDL"
 [47] "NCGTL9882590326460018406204203213632732966442UYAOIBDORZTIHLLGHPYKVVOKUNNJZKVYQWAZZVZHAABPFWCBBNKQLDJBEGFKPYSKIZTTVNKGRTQIHXGTNLYKEYHOGJYRMJDGACEO"
 [48] "CAZER3663023333686307941120889596025351029798RGCBSRXUEKUSJKVFSTTUCYXDQDTHXDUQGKPAJCVNDWQZAFUSNMQLSUUJQYWJQXTMDWGFEOFSFVTHKJLTAAKTMZGAARAQCTTKYASA"
 [49] "LUFGK2500055109148344838006592586379279469618VMENADFYUZRWTEYKMUSZWWNOARQPHCCZJLHANFTJRSHZNUMGOTFDAYLQLRMSEKICIRZVZALPOTITQFJBCLBEXAZFWNQHOFPBHPFJ"
 [50] "XVQNA6961018314091028543177708517936545299740JUNQLSHOZTUDBWGTHEHMGTHNGTFBVPNHGOLQDTHGGNATDHWDRLZGZSVMVRWWIVQIHBVQWHMPJHCNQZSIYSGGVBGOTOIYOYTBCHYU"
 [51] "RCDPV0600915984568662748323102309094538493202SHJZSJBQSBDMQTFCBESZBEKUWBFUNMMVCVKFNWVYIBUDDERPDYHNSDIEKKWAROSGSDPCCTFEZGQZJSHAFEXJSUBJIBAJSSNTOFNY"
 [52] "MIJTX2871208543737604239882163609993878660253GEOYFQTQCDPWCQYIUYLUBRQKWPOGETTRPRFFGRMPPLAXRHJFITUBYUJIANVVLHXMAXASUMXSOPWFYFMNKBTRBDJBENRKQABUVDIN"
 [53] "OHDHR0463406752401817577410199454642844369572GBHZKYGZVDEOFWKNDZYWEQLDXCOXPGNUJKUZBWNBIAPTDKBWYNHCFGRJOQCSGSNFNQCFIKSVQMBOPZWOFBVYPAKWMEAIPDJLTLEF"
 [54] "ZRRNR2378246902596608274227296227251733087093GATZPMNREXAMPOPOEIRLXDNIEQEIUTPQWROBJWKBWDOQMFXKNRRCBPDABKDZNSMTVYXMWRBIRYIJXBMXFAADEKABFQAURYCUGLFC"
 [55] "KKNLL1377283321831698169028947658602987161863HSXPTOMZLSNLUREAQEUHQJIENQMMGBIOABHSVHJIZRLTZEHXTZNPTZZWVGXNGGCJCWBJEZYHGFSBAABCVMJFVVHVJQPAJLGFIZLQ"
 [56] "VVEIV6564052169738907816093406549672819255229HXKTWOCDTXWTXJRBIZRNHYELGQZQJZZOUHWCRMKVYSIZFLFZOOUFPDATCPRAFTQFPVCXNKKXYTYBXDUPCWNDQXJZZEUPUPXFDKNZ"
 [57] "CNLNW1716972391548314590560678931279191684464NPDRDDGYOQCGTZOORHLGXUQKZEHUYQIGRIACDLTRNEPVICFKPZPLWTJRZDXCTKKCZVMJTSOSMZWUKUGPWIPVWOMUAQFGIJRZNHVI"
 [58] "NDMDX7591612308360380548289158585512624395768ZOURGCUHHSWMKJFPMVLZFKSJTXOJCQOAVFSDMIIUTJUFQHGZDBJHOHRPMSWKCQITVOJNQYITDKYDFSILHVSFHKEYOPBNHUEIOJUW"
 [59] "MATSC1591970396796665709400813646691199384041LBMLVYFWBKJJGKKBBKGAHYYUINAVETRJSLWKXITAZONZHRJFHDEIIKKNSTUPJOEQWMTUHQCWJVOYSSZPLYYLDVXKORRKUONJIWKE"
 [60] "SOMMU5021361263104822815484279275721209983552BKEEIERITYWVYKMVYKBXEUHHBIVSHTGCIBQDXZWJUWZUSKLBSEJQQXOHZEYFELZLXYYCMTQEBMJIRXXFLCKGSCGDXEPVLMFMOYXW"
 [61] "HOTCC8781091275141653825005044516923425173101ILRPLLXKIFGIVQWKUCZRGJUDXYKVMXNIBZULEMRKASEMZKNAEZHNBWIJYXEVEIFZBNWJNANOLJLHCDORFEKVUPAWOCAXODLEEUSU"
 [62] "IKHOW5888068838388896375263691739542413458914SNQJDCCSLLDSKGGQSUGZJUYZWMGLGMQOEBOXMTLIOOZVQFNOBDNCSGVHCPHJBCODMXGYWFWXKWRYSRXYKSNDJKVRPJIDUOUXYLEW"
 [63] "DMXBK5462447058520394658714436020783253143991YKZOJLTKWORRKXJVUQHGIOIGVGFIKTLIBFDNBKBSIZMDGLOJBGHBHEVSHZXWKGXAXXJVHKJLJOZWIQLYWYBHSRYEUTCHNMIGRTEM"
 [64] "QNFOH7801235878012262734478816993153923594205QJIUCKSLKSWXRBGUSYRCZTLWQUMNAFNKHRZEBZSFLXSCSLADQKAWUGPLDXDGPEPHNCVXLUQFNWPWUXKGZODSWOBLZVTXMLARYGII"
 [65] "EQYSA8392034899044198890891565218785068021301SSWGIBDPRGNLVSTTZEMYBMTTFAJBUXTCMYMXCVCFUKMFZTRBUFYOCAIBFAGPHXJTMBRJLUEKKJRPNOESILOZNBCCGWSIQHXEZDUW"
 [66] "DJFSE1272277395746494794548249998816566003059EOWLFUOPXZTQGRAUZWWWNQDNNOTSLUEPGPXEYUPGHESPSRHBWTQXFRCPBYXMBEXAZDHMQWMBERJBXZOKKIWIDZQFPUZTZJCSUYRY"
 [67] "ZOKQT0233651799493571118773931029363738564270RAGCZOXRGLJNKXAIEVJUXXZJUFAIXZCJFGBZHZZVCEFTQSBIBIESBAEKMPISDFQCGJLEYTYIINROPWHRIKFSXQBVPNTBGRCGRSOA"
 [68] "EISRR1208567586948073779156240698918844377823DUMHUXAXKTKUDMCJBWULIALQUPECPUSKNGNKMUQMTBIPRAANRTARPBXYVEOFDHMWWXCHUKZKEPCTPPGARFEYXYMBRCHNLFMTUDTQ"
 [69] "CXCPC3407753851378753276695923439588018884429QQBSPZTKRFYHXJDRCWQDFHYUFLVYTVQTBNRYMIHWOENLNCFPKDVLQUBPYSWSPINZVZROSTAVRNPCQKNBMSATJLVSJCTOCVAZECUB"
 [70] "JWGRA9518095826890092588380236834040122670899KRGYLLSFUSQKRJJUFQMEWOCJBPJBARGRIKFAMYBTAZQUXSUNBCOGCBDMCDQTDSLABXCYARYGWFBNERDIVPDMGQKUGUBUAJSJJLFA"
 [71] "VPRAK9039353981604290613068188497325075905762CRBGBRTGSYAIITYPMSPYLGMQIEUDKZDIEDGHCOCXCBTBRVXETICEYOGOGTRUALHXVNSTSWTBJUFECDEICCCAHGZZAIKACNTDYSMZ"
 [72] "NBWDQ2541665511022397554586193000504906014306FFPVZJYSFGFRWTWEBZXERXOWAFMDKHBZRZYMGMXHWBGUCAQPVWYZESJOCQIMAFLNHNHYHELLCVFNXAZDFUFXIACUEYEJCYDESNYF"
 [73] "SEDCX8691729965318809359172418725969366280077DSRNZHTXBLGFBAFAZBEFDAZWYNICUQVUUGEPKJFYXAORTWWFGMEEGSHFKKNJBGMYHCQJKERSMMDDBOKGRMEGPKTLXJYHGTWAYVVI"
 [74] "WKZWE0752679863398205999633000579342926986322HRDLNZNIERWGJNVHJGIUWBQRRBLIGJWCLRNZFVESUPFRQZXGYISYGYOSQCNWQHOCIOYUJFMOXPBDCIGWSDCAAKZBOIYXQHIEUPUF"
 [75] "MLUYU5263704595890281436545642862300178661552YMZEQKIKFONNNFYTSFCIQDHTSPRRGVCBOXNCUUYAIHGKDRBTQYYZOKFEOAPHUQOPNOCMHWRHSPEBFNBIGJCPMYOIIELNHBRBGJEI"
 [76] "VAMXK9279481762899564775623714880380036195115RXMVNEELFZODMCRMLIVMQRYJUDDDFRTXXYAFCTZWTTGWKJNVUGSXEDISVANBKPYLBOTKCJNPGWUHZUKMZJUPXBHOTJOKBMGNDLPC"
 [77] "AYNOJ6486857901077210743837784936885338063963DPRFSQWZSMXNXTOLNRTDJCIBPBQZCDFFDDYHUMVDSBNHZFRKHITUDGHOYXVXKTLPEPBZUHLPPTDPCXHVXJIPBHADVTSCPAPZCDXO"
 [78] "WGOGH3878336446071537219582968322363472092403RAJHLSFNKADUPTGYRQWDWRLTWGMIDLPZJBLNBHGTBVEITQYQQDIKLYDMLZBHTOAIFABQGYWHPUANXXZEJDTWUBOBZTKRPEXQTRIH"
 [79] "GKWSU9345538605961656977056446516047916015923QWHPVGBHRJCDIOTPAUSVJTODXRHGROXGUILPOJQHCLAAMHPLMQJEEHUIRAHCXCJKUKGXKEKSROZPZUEOBEAKZSZKZSMMLSHWLHIF"
 [80] "KEYZG5305971422048144681889610214375987253437EGJRGILIKXTKMKYEUFTLIIQFFWLYCRNQTFJBPCXGSMXDAVLELKLLJPNGIFLHCYRVISYUWOYEBUSELXGXVSDUKJJYUSLQYBXJGXMS"
 [81] "GWOIB0836628191244384108601230895311931050648DZDPNTZQCGDBYUDHNOYTUABKMSRESPRGQZCWTOWXZXDGXQOJADEWXNOJHFOGTCNXDKLPQNFDNTZJJBDDOHXTFPJKASWFXAKJFKHY"
 [82] "XXEGL0092904684587010560783743178697923627488LSMCLHFRWHSIRDTIXFIPQWYGFTYUWXWEUHZYHRNVVUPBLYMKUUEWQDWGKWGTTDFMRKEHYTHFHSYZCOVRTFXZUCSSIWGOAOKXKCQZ"
 [83] "PHKFM4066382062934597965904679170187555659437WKGJITHBHMKIVTLJRXEVLHTKWKOCLBSUOYHRPMQQEAEHETEYHDGBUJVSQINLXKMIXCHHPULYAHOYSDFQNOJFGTPGMGHLLBXCGHPS"
 [84] "NRFZH3289231997193221343040676370537892080990KPFEFWJPOCGILIAPRXEJWWGNIGSSOXVGJVHYJKHDFZMROTFSMBOXYPJBVGCRDTONSIXOZMOWDQVMFKPASLBBIOAKZKGVIHFVEUKQ"
 [85] "EYMVW0543258616222363553297893261061338958213PDJRLLOPGTMRTXWQINTGYWEJCYUQGQAPLRQTINLWLUCKIJRKSZWJIRGDHUKONQQZNDBCKJHQEEULHYUTHCXVTBEICEXSBDHNOVEZ"
 [86] "WWNBO7650790706194283694741181247885277170389EJYXTCJMJHWUSRJUDWMAHBIOXMVEVPTZXXVOFEIUABMAALWQBZSPKVKMNTDDHNIGFLUYNXJEAQVIJFCEUEOHRGDZQAQWMUJXRZJW"
 [87] "BZZGV8793839024042710216898640685126984776999IGRIQGPGIFTXTWIKAUJKFSCDYZDZHUEPHYRHGLAFAGESAJHJGTRZSXPMKJFXFWOPEHOQXWMWYYBAAVDVQWCBGAAIMHOKCPOUPZWT"
 [88] "YMGAY0070663785594559430227841464742779214107YZDXTYPAKKZECYAZHOBUYBKPWRBYDFKANZQUFSGHIWNQCUAPPKOORNHNCNTLPNMWCSWSBTIHEDPIWFLRDFLNPIOALJTWSTWCOYCU"
 [89] "LHIJO9252160166184756823838963402478484121746ASBLIMTIXPPTPIPRARMSEVKCROEWEBVQZBHMGVMKKEGNQQMMAZWXKVQHNZTJWTOSHSOTOJIJDSGBJEGVTDQUEXOIFSVCLNJTRCFR"
 [90] "SBDSV2862923129611624482317440654993364343478XCYHYTOCSVRGBBBQWOOPNFCOXRGJIHTOXKXNETUUHRQDVXCMODXWKCEGXQIKAFCKUGNVQTZWQDAXDEITBRZXOMMERGYDYMPGYFZJ"
 [91] "NEUDG1463992807395034459777110617798351515477ZKILJWGURULNWHJPULBTNKTTKJVJANEQDXWRTDXEZLIWEKMGVFWXDTDBSVUSGVCPPIYJICDTSCLJHVHKWXTGLTUQRBVIOBZZHGLJ"
 [92] "WEACD5221044260168865120706648077880402165314XGCJOAQFKAUKYVXWLGQLPPZIEGUGLKNZEYVCWHYKLHEPYSWUSNEAMAUMOFXVLDLPBUKQCLBWDLPZICPQKJQNPRLHEFPFTIUFIWGT"
 [93] "WBXJC1883599645090572177365689502697184704441YDAVVJYUWWQMYDETJIJENCNYVBARCJYRHDZPBXWESXZBPTOLPGZNWTUSMZOAQLFLFNVLQVJDLIQUOQBYINMRXQITQQVFUKSVBORW"
 [94] "OUQVZ0272663513510202543783813275994992774827HPEEMHDAYLOEFPKSRCSLMSVSHLCMTNTKWPQYDIWACANOWECKCHTZZXYMWASVZACTTPJIOEVANMRUPEKMYSJDZXXDJUEDAXBWTFRF"
 [95] "YWGOH1680500943047495168171842307761975528645XGBDFDJCSUKYURRMYECPZBYYWGBYZBFNWFBQOHAWTHCUQWTTIAZDHJLNQLOHYGEHNNNLAVAEPQOYJHVXMYFKHANPJUJSCFQRMQBV"
 [96] "MIEIS6816657804978054362384017418019265095410ZBULNUXLUOTWBKGTZCIXCMSCBXGMXIGKHRNPBATOAZVPKIGENVMDSATXWMWDENOGRCXDRPMGKPIJXLGLFHPIONHXSHXLACRZIRDL"
 [97] "OFSTJ9882590326460018406204203213632732966442UYAOIBDORZTIHLLGHPYKVVOKUNNJZKVYQWAZZVZHAABPFWCBBNKQLDJBEGFKPYSKIZTTVNKGRTQIHXGTNLYKEYHOGJYRMJDGACEO"
 [98] "BQPVK3663023333686307941120889596025351029798RGCBSRXUEKUSJKVFSTTUCYXDQDTHXDUQGKPAJCVNDWQZAFUSNMQLSUUJQYWJQXTMDWGFEOFSFVTHKJLTAAKTMZGAARAQCTTKYASA"
 [99] "EBKWH2500055109148344838006592586379279469618VMENADFYUZRWTEYKMUSZWWNOARQPHCCZJLHANFTJRSHZNUMGOTFDAYLQLRMSEKICIRZVZALPOTITQFJBCLBEXAZFWNQHOFPBHPFJ"
[100] "HVGOG6961018314091028543177708517936545299740JUNQLSHOZTUDBWGTHEHMGTHNGTFBVPNHGOLQDTHGGNATDHWDRLZGZSVMVRWWIVQIHBVQWHMPJHCNQZSIYSGGVBGOTOIYOYTBCHYU"

  [1] "IGKFE8978657113260663000555517663634048521293TANMEKANLQQQCAKYFGKUPXCFWPQKLJHDPADBTKAKHEMPUHRLXMCKMGWUAZJZHAVOOAECONVAFHBOIYXZMBNCAZZOHNGQHCDWVGNS"
  [2] "ITXKT8299552616876567235269466322051167885568KUOSKXWCAVPMBDBHUJCGZFPEDPZFZUMBYUNYYGWKOZUWGFWLTGDBHFOTYWWIUBRSYTKDFKNGBABIFNGMNNAZAJAVKFXUEHJBOAOJ"
  [3] "PBGDQ4140563402589773522626325573502911292227KVAQUJLQFJKHLCGPHNYZBLGLVDRFKAOGEQXMLLODHBOGMBWWLRSXCTBDZQVLTFFLWEFVLACQVUDCXDIYXROTVFUIFAPPAJUDNCFO"
  [4] "OAKAE8456298670500788743674350163819634033867YQANIIMBHGJVHNOVKGSKHQXQTZFVWQHFKPVKNSAXOXSOITYCLNTWGLCWLSRKZNMPOLKZXOVOTNOWNHOSTZAIPPHDYMNGKYLPTMOU"
  [5] "UKYZP6960489080608397778607224027891497232138YBCFMUGRHYZOAQESSICRCAUPARIQYXUAMRIGJPSHQTUJYWUBUEWTBXWFVHHSOWCPOXRPEGBIETSFYTNTJRSCHJQLVWVAQSACPZRP"
  [6] "GEEMT2250262488578238823104793509690470119945ZGHLXCCFMPVISQOEZFELTCQXHHJNZLUDPUBBCSLMJRDOMNMDAPTYVMEWYHNUMRJJPPEEBOCUBGINTBTLTSDVRKPXYSYXNPZBRVBQ"
  [7] "AUAKA0369950297924768937621451030896867387971KGVXPMXFVCJRQZICRWAEYC